
\begin{thebibliography}{99}
\bibitem{templar}
    Borók-Nagy, Z., Májer, V., Mihalicza, J., Pataki, N., Porkoláb, Z.:
    \textit{Visualization of C++ Template Metaprograms} SCAM(p./pp. 167-176),
    In: IEEE Computer Society. ISBN: 978-0-7695-4178-5 (2010)
\bibitem{templight}
    Borók-Nagy, Z., Porkoláb, Z., Mihalicza, J.:
    \textit{Templight}:
    \burl{http://plc.inf.elte.hu/templight/} (2014. October 11.)
\bibitem{generative-programming}
    Czarnecki, K., Eisenecker, U. W.:
    \textit{Generative Programming: Methods, Tools and Applications},
    Addison-Wesley Professional; 1 edition (2000) ISBN:0201309777
\bibitem{cpp14}
    International Standard Organization, International Electrotechnical
    Commission: \textit{ISO/IEC 14882:2014(E) Programming Language C++}
\bibitem{mihalicza-phd}
    Mihalicza, J.:
    \textit{Analysis and Methods for Supporting Generative Metaprogramming in
    Large Scale C++ Projects}, PhD thesis (2014)
\bibitem{persson-templight}
    Persson, S. M.:
    \textit{Templight fork and related tools}:
    \burl{https://github.com/mikael-s-persson/templight}
    (2014. December 6.)
\bibitem{functional-programming-cefp}
    Porkoláb, Z.:
    \textit{Functional Programming with C++ Template Metaprograms}.
    In: Proceedings of the Third Summer School Conference on
    Central European Functional Programming School. CEFP’09, Berlin,
    Heidelberg, Springer-Verlag (2010)
\bibitem{just}
    Sinkovics, Á.:
    \textit{Just C++ libraries}:
    \burl{https://github.com/sabel83/just} (2014. October 11.)
\bibitem{sinkovics-phd}
    Sinkovics, Á.:
    \textit{The connection between C++ template metaprogramming and functional
    programming}, PhD thesis (2013)
\bibitem{meeting-cpp}
    Sinkovics, Á., Kucsma, A.:
    \textit{Interactive Metaprogramming Shell Based on Clang}, In:
    Meeting C++ conference, Berlin 2014, December 6.:
    \burl{http://meetingcpp.com/index.php/tv14/items/12.html}
    (2014. December 7.)
\bibitem{github}
    Sinkovics, Á., Kucsma, A.:
    \textit{Metashell}:
    \burl{https://github.com/sabel83/metashell} (2014. November 11.)
\bibitem{cpp-meetup}
    Sinkovics, Á., Kucsma, A.:
    \textit{Template Metaprogramming With Better Tools}, In: Hungarian C++
    Community Meetup, Budapest 2014. December 1.:
    \burl{http://www.meetup.com/Hungarian-Cpp-Community/events/218043432/}
    (2014. December 2.)
\bibitem{using-cpp-metaprograms}
    Veldhuizen, T.:
    \textit{Using C++ Template Metaprograms} In: C++ gems, Stanley B. Lippman
    (Ed.). Sigs Reference Library Series, Vol. 5. SIGS Publications, Inc.,
    New York, NY, USA 459-473. (1996)

%link only bibs

\bibitem{boost}
    \textit{Boost C++ libraries}:
    \burl{http://www.boost.org/} (2014. October 11.)
\bibitem{boost-fs}
    \textit{Boost.FileSystem}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/filesystem/doc/index.htm}
    (2014. December 1.)
\bibitem{boost-graph}
    \textit{The Boost Graph Library}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/graph/doc/}
    (2014. December 1.)
\bibitem{boost-lexicalcast}
    \textit{Boost.Lexical\_Cast}:
    \burl{http://www.boost.org/doc/libs/1_57_0/doc/html/boost_lexical_cast.html}
    (2014. December 1.)
\bibitem{boost-mpl}
    \textit{The Boost MPL library}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/mpl/doc/refmanual.html}
    (2014. December 7.)
\bibitem{boost-mpl-metafunction}
    \textit{Metafunction definition from the Boost MPL library}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/mpl/doc/refmanual/metafunction.html}
    (2014. December 7.)
\bibitem{boost-optional}
    \textit{Boost.Optional}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/optional/doc/html/index.html}
    (2014. December 1.)
\bibitem{boost-pt}
    \textit{Boost.PropertyTree}:
    \burl{http://www.boost.org/doc/libs/1_57_0/doc/html/property_tree.html}
    (2014. December 1.)
\bibitem{boost-regex}
    \textit{Boost.Regex}:
    \burl{http://www.boost.org/doc/libs/1_57_0/libs/regex/doc/html/index.html}
    (2014. December 1.)
\bibitem{boost-spirit}
    \textit{The Boost Spirit Library}:
    \burl{http://www.boost-spirit.com/} (2014. November 29.)
\bibitem{boost-string}
    \textit{Boost String Algorithms Library}:
    \burl{http://www.boost.org/doc/libs/1_57_0/doc/html/string_algo.html}
    (2014. December 1.)
\bibitem{clang}
    \textit{Clang}:
    \burl{http://clang.llvm.org/} (2014. October 11.)
\bibitem{cmake}
    \textit{CMake}:
    \burl{http://www.cmake.org/}
    (2014. December 2.)
\bibitem{gdb}
    \textit{GDB: The GNU Project Debugger}:
    \burl{http://www.gnu.org/software/gdb/}
    (2014. December 1.)
\bibitem{graphviz}
    \textit{Graphviz - Graph Visualization Software}:
    \burl{http://www.graphviz.org/} (2014. December 8.)
\bibitem{libclang}
    \textit{libclang: C Interface to Clang}:
    \burl{http://clang.llvm.org/doxygen/group__CINDEX.html} (2014. December 8.)
\bibitem{github-releases}
    \textit{Metashell's Releases page on Github}:
    \burl{https://github.com/sabel83/metashell/releases} (2014. December 8.)
\bibitem{qt}
    \textit{Qt Project}
    \burl{http://qt-project.org/} (2014. December 8.)
\bibitem{readline}
    \textit{The Readline library}:
    \burl{http://cnswww.cns.cwru.edu/php/chet/readline/rltop.html}
    (2014. October 11.)
\end{thebibliography}
