\documentclass[a4paper,12pt]{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\frenchspacing
\usepackage{lmodern}

\usepackage[margin=2.5cm,left=3.5cm,includeheadfoot]{geometry}

\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{float}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\lstloadlanguages{C++}
\lstset{
    stepnumber=1,
    numbers=left
}
\lstdefinestyle{customcpp}{
    belowcaptionskip=1\baselineskip,
    breaklines=true,
    frame=L,
    xleftmargin=\parindent,
    language=C++,
    showstringspaces=false,
    basicstyle=\footnotesize\ttfamily,
    keywordstyle=\bfseries\color{green!40!black},
    commentstyle=\itshape\color{purple!40!black},
    identifierstyle=\color{blue},
    stringstyle=\color{orange}
}
\lstdefinestyle{mdboutput}{
    belowcaptionskip=1\baselineskip,
    breaklines=true,
    frame=L,
    xleftmargin=\parindent,
    language=C++,
    showstringspaces=false,
    basicstyle=\footnotesize\ttfamily\sffamily\mdseries,
}
%\lstset{escapechar=@,style=customcpp}
\newcommand{\includecode}[1]{
    \lstinputlisting[escapechar=, style=customcpp]{#1}
}

\usepackage{graphicx}
\usepackage{setspace}
\onehalfspacing

\begin{document}


\input{tex/cover}


\vspace*{\fill}
\begin{center}
%TODO Temabejelento
\end{center}
\vfill
\thispagestyle{empty}
\newpage
\setcounter{page}{1}

\tableofcontents

% TODO maybe \include is better?
% http://en.wikibooks.org/wiki/LaTeX/Modular_Documents#Getting_LaTeX_to_process_multiple_files
\input{tex/introduction}

\input{tex/userdoc}

\input{tex/devdoc}

\input{tex/testing}

\input{tex/summary}

\input{tex/relatedwork}

\begin{thebibliography}{9}
\bibitem{github}
    Sinkovics, Á., Kucsma, A.:
    \textit{Metashell's Github page}
    \url{https://github.com/sabel83/metashell} (2014. November 11.)
\bibitem{sinkovics-phd}
    Sinkovics, Á.:
    \textit{The connection between C++ template metaprogramming and functional
    programming} (2013)
\bibitem{mihalicza-phd}
    Mihalicza, J.:
    \textit{Analysis and Methods for Supporting Generative Metaprogramming in
    Large Scale C++ Projects} (2014)
\bibitem{boost}
    \textit{Boost C++ libraries}
    \url{http://www.boost.org/} (2014. October 11.)
\bibitem{boost-spirit}
    \textit{The Boost Spirit Library}
    \url{http://www.boost-spirit.com/} (2014. November 29.)
\bibitem{boost-graph}
    \textit{The Boost Graph Library}
    \url{http://www.boost.org/doc/libs/1_57_0/libs/graph/doc/}
    (2014. December 1.)
\bibitem{boost-optional}
    \textit{Boost.Optional}
    \url{http://www.boost.org/doc/libs/1_57_0/libs/optional/doc/html/index.html}
    (2014. December 1.)
\bibitem{boost-pt}
    \textit{Boost.PropertyTree}
    \url{http://www.boost.org/doc/libs/1_57_0/doc/html/property_tree.html}
    (2014. December 1.)
\bibitem{boost-regex}
    \textit{Boost.Regex}
    \url{http://www.boost.org/doc/libs/1_57_0/libs/regex/doc/html/index.html}
    (2014. December 1.)
\bibitem{boost-fs}
    \textit{Boost.FileSystem}
    \url{http://www.boost.org/doc/libs/1_57_0/libs/filesystem/doc/index.htm}
    (2014. December 1.)
\bibitem{boost-string}
    \textit{Boost String Algorithms Library}
    \url{http://www.boost.org/doc/libs/1_57_0/doc/html/string_algo.html}
    (2014. December 1.)
\bibitem{boost-lexicalcast}
    \textit{Boost.Lexical\_Cast}
    \url{http://www.boost.org/doc/libs/1_57_0/doc/html/boost_lexical_cast.html}
    (2014. December 1.)
\bibitem{just}
    Sinkovics, Á.:
    \textit{Just C++ libraries}
    \url{https://github.com/sabel83/just} (2014. October 11.)
\bibitem{clang}
    \textit{Clang}
    \url{http://clang.llvm.org/} (2014. October 11.)
\bibitem{templight}
    Borók-Nagy, Z., Porkoláb, Z., Mihalicza, J.:
    \textit{Templight}
    \url{http://plc.inf.elte.hu/templight/} (2014. October 11.)
\bibitem{readline}
    \textit{The Readline library}
    \url{http://cnswww.cns.cwru.edu/php/chet/readline/rltop.html}
    (2014. October 11.)
\bibitem{gdb}
    \textit{GDB: The GNU Project Debugger}
    \url{http://www.gnu.org/software/gdb/}
    (2014. December 1.)
\end{thebibliography}

\end{document}
